Package Documentation

### 2022-07-04 quarto-doc/pkg_doc.qmd
Minor update. Re #97

number-sections: true
crossref:
  chapters: true

---

@@

+---------------+----------------------+----------------------+
| Label         | Name                 | Levels               |
+===============+======================+======================+
| *a*           | Age group            | 15--49\              |
|               |                      | 50--69               |
+---------------+----------------------+----------------------+
| *g*           |                      | Male\                |
|               |                      | Female               |
+---------------+----------------------+----------------------+
| *h*           | Disease              |                      |
+---------------+----------------------+----------------------+
| *i*           | Individual index     |                      |
+---------------+----------------------+----------------------+
| *j*           | Trip index           |                      |
+---------------+----------------------+----------------------+
| *m*           | Transport mode       | walk\                |
|               |                      | cycling (cyc.)\      |
|               |                      | bus\                 |
|               |                      | car\                 |
|               |                      | motorbike (mot.)\    |
|               |                      | goods vehicles (GV)\ |
|               |                      | subway (sub.)        |
+---------------+----------------------+----------------------+
| *o*           | Outcome              | Death\               |
|               |                      | YLL                  |
+---------------+----------------------+----------------------+
| *s*           | Scenario             | 3                    |
+---------------+----------------------+----------------------+
| *w*           | AP RR hyperparameter | 1, 2, 3, 4           |
+---------------+----------------------+----------------------+
| *x*           | PA RR hyperparameter | 1, 2, 3              |
+---------------+----------------------+----------------------+
| *z*           | PA dose              |                      |
+---------------+----------------------+----------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+:==========================================+=================================================================+:===================================+===============================+====================+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $I _ {a,g,m_{\                            | Fatalities table                                                | Constant                           | INJURY_TABLE                  | Setting            |
| text{vi c} },m_{\text{str}}}$             |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\                                        | Vehicle emission inventory                                      | Constant or Dirichlet              | EMISSION_INVENTORY            | Setting            |
| g amma_{m}$                               |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\                                        | Quantiles for AP RR functions                                   | 0.5 or Unif(0,1)                   | AP_DOSE_R ESPONSE\_ QUANTILE  | Model              |
| xi_{h,w}$                                 |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\                                        | Confidence in PA survey                                         | 1                                  | BACKGROUND_PA_C ONFIDENCE     | Setting            |
| tilde{Y}$                                 |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\lambda_{m\not\in\text{wal               | In-vehicle MET surplus                                          | 0                                  |                               | Model              |
| k,cyc.}}$                                 |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

[Note on recategorization]{.ul}: for some of the modes (like for car, bus, motorcycle and cycle), if both strike and victim modes are same, we explicitly make the strike mode as 'noov'

@@

+:----------------------------------------------------------------------------------:+:---------------------------------------------------------------------------------:+
| ![100 samples from AP dose--response curves](cvd_ihdDR-sim.pdf){#APDR width="40%"} | \[100 samples from AP dose--response curves\] (cvd_strokeDR-sim.pdf){width="40%"} |
+------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+

+:-----------------------------------------------------------------:+:------------------------------------------------------------:+:------------------------------------------------------------------:+
| ![100 samples from AP dose--response curv es](neo_lungDR-sim.pdf) | ![100 samples from AP dose--response c urves](lriDR-sim.pdf) | ![100 samples from AP dose--response curve s](resp_copdDR-sim.pdf) |
+-------------------------------------------------------------------+--------------------------------------------------------------+--------------------------------------------------------------------+

::: landscape
# Tabulated ITHIM equations {#tableequations}

>>>>

number-sections: true
crossref:
  chapters: true
---

@@

+-------+----------------------+----------------------+
| Label | Name                 | Levels               |
+=======+======================+======================+
| *a*   | Age group            | 15--69\              |
|       |                      | (five years age      |
|                              |             group)   |
|                              |                      |       
+-------+----------------------+----------------------+
| *g*   |                      | Male\                |
|       |                      | Female               |
+-------+----------------------+----------------------+
| *h*   | Disease              |                      |
+-------+----------------------+----------------------+
| *i*   | Individual index     |                      |
+-------+----------------------+----------------------+
| *j*   | Trip index           |                      |
+-------+----------------------+----------------------+
| *m*   | Transport mode       | walk\                |
|       |                      | cycling (cyc.)\      |
|       |                      | bus\                 |
|       |                      | car\                 |
|       |                      | motorbike (mot.)\    |
|       |                      | goods vehicles (GV)\ |
|       |                      | subway (sub.)        |
+-------+----------------------+----------------------+
| *o*   | Outcome              | Death\               |
|       |                      | YLL                  |
+-------+----------------------+----------------------+
| *s*   | Scenario             | 3                    |
+-------+----------------------+----------------------+
| *w*   | AP RR hyperparameter | 1, 2, 3, 4           |
+-------+----------------------+----------------------+
| *x*   | PA RR hyperparameter | 1, 2, 3              |
+-------+----------------------+----------------------+
| *z*   | PA dose              |                      |
+-------+----------------------+----------------------+

@@

@@

|:-----------------------------------------------|-----------------------------------------------------------------|:-----------------------------------|-------------------------------|--------------------|

@@

| $I _ {a,g,m_{\   text{vi c} },m_{\text{str}}}$ | Fatalities table                                                | Constant                           | INJURY_TABLE                  | Setting            |

@@

| $\   g amma_{m}$                               | Vehicle emission inventory                                      | Constant or Dirichlet              | EMISSION_INVENTORY            | Setting            |

@@

| $\   xi_{h,w}$                                 | Quantiles for AP RR functions                                   | 0.5 or Unif(0,1)                   | AP_DOSE_R ESPONSE\_ QUANTILE  | Model              |

@@

| $\   tilde{Y}$                                 | Confidence in PA survey                                         | 1                                  | BACKGROUND_PA_C ONFIDENCE     | Setting            |

@@

| $\lambda_{m\not\in\text{wal                    
  k,cyc.}}$                                      | In-vehicle MET surplus                                          | 0                                  |                               | Model              |

@@

[Note on recategorization]{.underline}: for some of the modes (like for car, bus, motorcycle and cycle), if both strike and victim modes are same, we explicitly make the strike mode as 'noov'

@@

|                                                                                    |                                                                                   |
|:----------------------------------------------------------------------------------:|:---------------------------------------------------------------------------------:|
| ![100 samples from AP dose--response curves](cvd_ihdDR-sim.pdf){#APDR width="40%"} | \[100 samples from AP dose--response curves\] (cvd_strokeDR-sim.pdf){width="40%"} |

|                                                                   |                                                              |                                                                    |
|:-----------------------------------------------------------------:|:------------------------------------------------------------:|:------------------------------------------------------------------:|
| ![100 samples from AP dose--response curv es](neo_lungDR-sim.pdf) | ![100 samples from AP dose--response c urves](lriDR-sim.pdf) | ![100 samples from AP dose--response curve s](resp_copdDR-sim.pdf) |

::: landscape \# Tabulated ITHIM equations {#tableequations}
